%-------------------------
% Resume in Latex
% Author : Ethan Loo
% Based off of: https://github.com/shiloh4/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  \vspace*{-25pt}
    \textbf{\huge \scshape Ethan Loo}
  \vspace*{-9pt}
\end{center}

\begin{center}
  % \vspace{10pt}
\small 470-301-5218 $|$
\href{mailto:ethanlooyt@gmail.com}{\underline{ethanlooyt@gmail.com}} $|$
\href{https://www.linkedin.com/in/ethan-loo-73a1b0236/}{\underline{linkedin.com/in/ethan-loo-73a1b0236/}} $|$
\href{https://shiloh4.github.io/}{\underline{shiloh4.github.io}}
\vspace*{-10pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {BS Computer Science - CGPA: 3.84}{May 2022 - May 2026 (anticipated)}
  \resumeSubHeadingListEnd

  %-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Keysight Technologies $|$ Eggplant}{Penang, MY}
    {QA Engineer Intern}{May 2024 - Aug. 2024}
    \resumeItemListStart
      \resumeItem{Authored and debugged automated model-based and script-based test scripts in Eggplant Functional. Discovered 4 breaking bugs and led development of automated MBT tests for the respective test cases. Wrote approximately 300 lines of code in SenseTalk.}
      \resumeItem{Spearheaded the development and implementation of front-end, back-end, and other test procedures (\textbf{Cypress tests}, API/BDD tests, MBT tests) for new systems and application features under development.}
      \resumeItem{Collaborated in defining the minimum viable product (MVP) for Eggplant DAI version 7.5.0-0.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------Projects-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Connect-RX (HackGT11)}{\textit{React-Native}}
    {}{}
    \resumeItemListStart
    \vspace{-5mm}
      \resumeItem{Developed a cross-platform medication adherence tracking app using React Native app for patients and React app for doctors, tackling the issue of medication non-adherence.}
      \resumeItem{Leveraged ngrok to securely expose our Flask API backend, enabling seamless communication between the React Native mobile app and the React web app for real-time testing and integration.}
      \resumeItem{Designed and integrated a SQLite database to manage and store patient medication records, ensuring reliable data persistence across devices.}
      \resumeItem{Handled push notifications and reminders for patients based on prescription schedules received from the React app. Implemented a streak counter feature in the React Native app to gamify and reward patients for adherence.}
    \resumeItemListEnd

    \resumeSubheading
    {CompViz (Create-X $|$ launchny)}{\textit{React}}
    {}{}
    \resumeItemListStart
    \vspace{-5mm}
      \resumeItem{\textbf{Founding member} of a Django-based application that analyzes over 15,000 accounting metrics, providing insights to small businesses by comparing against consolidated anonymized industry data and publicly available data.}
      \resumeItem{Led the development of the frontend in React, using tools like Figma to draft a visually appealing and intuitive website design. Responsible for connecting the React frontend to Django backend endpoints to pull external data.}
      \resumeItem{Implemented integrations with FRED, EDGAR, and QuickBooks to incorporate micro, macro, and alternative data sources into the app.}
    \resumeItemListEnd

    \resumeSubheading
    {AgentArena (AI ATL 2024)}{\textit{React}}
    {}{}
    \resumeItemListStart
    \vspace{-5mm}
      \resumeItem{Developed a web-based LLM simulation platform using React for the frontend and Flask for the backend, enabling users to simulate and analyze agent interactions in multi-agent scenarios (Prisonners' Dilemma). Utilized Fetch API and React Hooks to dynamically fetch and update game state data in real-time.}
      \resumeItem{Leveraged Plotly.js for interactive data visualization, displaying agent performance metrics such as \textbf{niceness, forgiveness, retaliatory, troublemaking, and emulative behavior} over multiple simulation rounds.}
    \resumeItemListEnd
  
    % \resumeSubheading
    %   {Spotify Wrapped Application}{\textit{Android Studio $|$ Kotlin, Java}}
    %   {}{}
    %   \resumeItemListStart
    %   \vspace{-5mm}
    %     \resumeItem{Developed an application using Kotlin for both the frontend and backend, integrating Spotify API and Firebase to retrieve, store, and deliver personalized music analytics.}
    %     \resumeItem{Led the design and implementation of UI/UX, creating an interactive and visually engaging user interface.}
    %   \resumeItemListEnd

    \resumeSubheading
      {Vertically Integrated Project: Video Game for Power Grids}{\textit{Unity $|$ C\#}}
      {}{}
      \resumeItemListStart
      \vspace{-5mm}
        \resumeItem{Developed and maintained Azure server with a focus on secure Gurobi API endpoints, efficient concurrency handling, and thread-safe configuration, ensuring high-performance and reliable data management for optimization simulations. Used an \textbf{ASP.NET Core controller to handle HTTP Post requests}.}
        \resumeItem{Directed planning and development of UI/UX design for the video game using pixel/3D rendering software like Aseprite and MagicaVoxel.} 
    \resumeItemListEnd
      
    % \resumeSubheading
    %   {Quantum (2D Pixel Platformer)}{\textit{Unity $|$ C\#}}
    %   {}{}
    %   \resumeItemListStart
    %   \vspace{-5mm}
    %     \resumeItem{Led UI design and development, ensuring a seamless user experience and enhancing user accessibility and intuitiveness. Developed game assets and animation using Aseprite and Unity.}
    %   \resumeItemListEnd

    % \resumeSubheading
    %   {Minerva OCR \& Multimodal (DuckAI)}{\textit{TKinter}}
    %   {}{}
    %   \resumeItemListStart
    %   \vspace{-5mm}
    %     \resumeItem{Spearheaded development of GUI for eye-tracking data visualization, developing 3 designs prototypes using TKinter.}
    % \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------Skills and Interest-----------
\section{Skills \& Technical Experience}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
  \vspace{1mm}
    \textbf{Languages/Frameworks}{: \textbf{HTML}, \textbf{CSS}, \textbf{JavaScript}, \textbf{React}, React-Native, Java, \textbf{Python}, C, C\#, SQL} \\
    \vspace{1mm}
    \textbf{Software Applications}{: Android Studio, Firebase, Docker, PopSQL, Unity, Figma, MagicaVoxel, Aseprite, Affinity Suite, Microsoft Excel, Tableau, \textbf{Atlassian (Jira, Confluence)}} \\
  %  \vspace{1mm}
  %  \textbf{Interests}{: Web Development/Design, Game Development/Design, Data Science, Graphic Design, Photography} \\
  }}
\end{itemize}


%-----------Courses-----------
% \section{Classes}
% \begin{itemize}[leftmargin=0.15in, label={}]
%    \small{\item{
%    \vspace{1mm}
%     \textbf{Relevant Courses}{: Data Structures and Algorithms, Computer Organization and Programming, \textbf{Design and Analysis of Algorithms}, Procedural Content Generation, Computer Graphics, \textbf{Systems and Networks}, Statistics and Applications} \\

%    }}
% \end{itemize}


%-----------Leadership-----------
\section{Leadership}
    \resumeSubHeadingListStart
      \resumeSubheading
      {Georgia Tech Malaysia Student Association}{\textit{Jan. 2023 - May 2024}}
      {Head of Outreach}{}
      \resumeItemListStart
      % \vspace{-4mm}
        \resumeItem{Designed impactful social media content and graphic designs using Affinity Photo and Designer, boosting Instagram engagement by 6\%.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
    % \vspace{8pt}
    % \resumeSubHeadingListStart
    %   \resumeSubheading
    %   {Reformed University Fellowship}{Jan. 2024 - Present}
    %   {Graphic Designer}{}
    %   \resumeItemListStart
    %   %\vspace{-4mm}
    %     \resumeItem{Created compelling graphic designs for RUF social media and event promotions using Affinity Photo and Designer.}
    %   \resumeItemListEnd
    % \resumeSubHeadingListEnd
    % \vspace{-12pt}
    \resumeSubHeadingListStart
    \vspace{-8pt}
      \resumeSubheading
      {Extracurricular Achievements:}{}
      {}{}
      \resumeItemListStart
      \vspace{-5mm}
        \resumeItem{Achieved 1st Degree Black Belt in Taekwondo ITF.}
        \resumeItem{Achieved PADI Open Water and Advanced Open Water Diver License.}
        \resumeItem{Completed BWC (Basic Wall Course) top rope sport climbing certification.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}